Hydrodynamics and rheology of weakly adhesive vesicle doublets

### 2019-01-30 vesicle_code/docs/adhesion/adhesion.tex
bib updated by yny

%
% for example, 
%it was shown recently that vesicles may align to form chains along the direction of the externally applied DC electric field with ensuing consequences to suspension rheology \cite{wu2018pairwise}.
%
Collective hydrodynamics of vesicles is dictated by the individual
vesicle-vesicle interactions.  
In a quiescent flow,
vesicle-vesicle adhesion leads to formation of vesicle doublets \cite{ZiherlSvetina2007_PNAS} or clusters \cite{SvetinaZiherl2008_Bioelectrochemistry,FlormannAouane2017_SciReports}.
As a model for red blood cell (RBC) aggregates, an idealized model for adhesive vesicle-vesicle interactions gives rise to 
vesicle configurations similar to those observed in experiments of fibrinogen-induced RBC aggregates \cite{SvetinaZiherl2008_Bioelectrochemistry,FlormannAouane2017_SciReports}. 
Using the L-J potential for point-point interaction between two vesicle membranes without the detailed molecular details of
adhesive interactions between RBCs, Flormann {\it et al.} found the contact zone to buckle under strong adhesion \cite{FlormannAouane2017_SciReports}. 
A direct consequence of the buckling is the
sigmoidal shape of the adhesion region, which is also observed in RBC doublets and explained in a slightly different model \cite{ZiherlSvetina2007_PNAS}. 
It remains unknown how adhesive interactions between vesicles might lead to different vesicle hydrodynamics that results in
different rheological properties of a vesicle suspension. Such studies will provide useful insight to the rheology of blood flow and how to use nano solutes to control the hypertension
by adjusting the adhesive interactions between RBCs.
%

In numerical simulations of  a vesicle suspension, the adhesive interaction between two vesicles is often ignored \cite{Veerapaneni2009_JCP,RahimianVeerapaneniBiros2010_JCP} 
for numerical convenience
because a smaller time step is often needed to resolve the dynamics of the lubrication thin film between two membranes with adhesion than without.
However, adhesive interactions  between RBCs lead to different RBC clusters that are expected to alter the rheological properties of the RBC suspension \cite{NeuMeiselman2002_BiophysJ,SvetinaZiherl2008_Bioelectrochemistry}.
Hydrodynamic simulations of adhesive vesicles in a quiescent flow have revealed physical insights to the equilibrium shapes of RBC aggregates in both experiments 
\cite{FlormannAouane2017_SciReports} and theory \cite{ZiherlSvetina2007_PNAS}. The main goal in this work is to investigate the hydrodynamics of adhesive vesicles in flowing
conditions common in microfluidic vesicle flow, such as a planar shear flow or an extensional flow.

@@

In our formulation we did not include any electrostatic interactions
between membranes under adhesion. When the electrostatic interaction is
important, an electro-osmotic pressure in the thin film is found to be
responsible for the observed membrane undulation~\cite{LiraDimova}.

>>>>

%
% for example, 
%it was shown recently that vesicles may align to form chains along the direction of the externally applied DC electric field with ensuing consequences to suspension rheology \cite{wu2018pairwise}.
%
Collective hydrodynamics of vesicles is dictated by the individual
vesicle-vesicle interactions.  
In a quiescent flow,
vesicle-vesicle adhesion leads to formation of vesicle doublets \cite{Ziherl2007_PRL,ZiherlSvetina2007_PNAS} or clusters \cite{SvetinaZiherl2008_Bioelectrochemistry,FlormannAouane2017_SciReports}.
As a model for red blood cell (RBC) aggregates, an idealized model for adhesive vesicle-vesicle interactions gives rise to 
vesicle configurations similar to those observed in experiments of fibrinogen-induced RBC aggregates \cite{SvetinaZiherl2008_Bioelectrochemistry,FlormannAouane2017_SciReports}. 
Using the L-J potential for point-point interaction between two vesicle membranes without the detailed molecular details of
adhesive interactions between RBCs, Flormann {\it et al.} found the contact zone to buckle under strong adhesion \cite{FlormannAouane2017_SciReports}. 
A direct consequence of the buckling is the
sigmoidal shape of the adhesion region, which is also observed in RBC doublets and explained in a slightly different model \cite{ZiherlSvetina2007_PNAS}. 
It remains unknown how adhesive interactions between vesicles might lead to different vesicle hydrodynamics that results in
different rheological properties of a vesicle suspension. Such studies will provide useful insight to the rheology of blood flow and how to use nano solutes to control the hypertension
by adjusting the adhesive interactions between RBCs.
%

In numerical simulations of  a vesicle suspension, the adhesive interaction between two vesicles is often ignored \cite{Veerapaneni2009_JCP,RahimianVeerapaneniBiros2010_JCP} 
for numerical convenience
because a smaller time step is often needed to resolve the dynamics of the lubrication thin film between two membranes with adhesion than without.
However, adhesive interactions  between RBCs lead to different RBC clusters that are expected to alter the rheological properties of the RBC suspension \cite{NeuMeiselman2002_BJ,SvetinaZiherl2008_Bioelectrochemistry}.
Hydrodynamic simulations of adhesive vesicles in a quiescent flow have revealed physical insights to the equilibrium shapes of RBC aggregates in both experiments 
\cite{FlormannAouane2017_SciReports} and theory \cite{ZiherlSvetina2007_PNAS}. The main goal in this work is to investigate the hydrodynamics of adhesive vesicles in flowing
conditions common in microfluidic vesicle flow, such as a planar shear flow or an extensional flow.

@@

In our formulation we did not include any electrostatic interactions
between membranes under adhesion. When the electrostatic interaction is
important, an electro-osmotic pressure in the thin film is found to be
responsible for the observed membrane undulation~\cite{SteinkuhlerAgudo-Canalejo2016_BJ}.
